\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-08 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
adding IEEE 14 bus sim results

\subsubsection{Contributions of this paper}
Our contributions are twofold. {\red{TBD}}

Our technical approach juxtaposes with the existing literature discussed above, in that we approximate neither the dynamical nonlinearity nor the statistics. Instead of treating the exact nonlinearity as bane, we exploit the geometry induced by the power system's dynamical nonlinearity over the manifold of time-varying joint state PDFs, thereby enabling a new proximal algorithm to compute the transient joint PDFs.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.95\linewidth]{IEEE14marginals.png}
\caption{\small{Time evolution of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs, where $i=1,\hdots,5$, for the Kron-reduced IEEE 14 bus simulation setup described in Sec. \ref{subsec:NumSimIEEEBus}. The $5$ rows above correspond to the $5$ generator nodes; these are buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. The columns correspond to the time snapshots. The colorbar at the bottom shows the marginal PDF values.}}
\vspace*{-0.1in}
\label{fig:IEEE14marginals}
\end{figure*}

@@

@@

\bibitem{mardia2009directional}
K.V.~Mardia, and P.E.~Jupp, \emph{Directional Statistics}, John Wiley \& Sons, 2009.

>>>>

\subsubsection{Contributions of this paper}
Our main contribution is to demonstrate that by harnessing recent developments in generalized gradient flows \cite{ambrosio2008gradient} and proximal algorithms \cite{parikh2014proximal}, it is possible to perform \emph{nonparametric} propagation of the joint state PDFs subject to the stochastic nonlinear dynamics of a networked power system, and that the computation can be implemented in a gridless and scalable manner.

Our technical approach juxtaposes with the existing power systems literature discussed above, in that we approximate neither the dynamical nonlinearity nor the statistics. Instead of treating the exact nonlinearity as bane, we exploit the geometry induced by the power system's dynamical nonlinearity over the manifold of time-varying joint state PDFs, thereby enabling a new proximal algorithm to compute the transient joint PDFs.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\linewidth]{IEEE14marginals.png}
\caption{\small{Time evolution of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs, where $i=1,\hdots,5$, for the Kron-reduced IEEE 14 bus simulation setup described in Sec. \ref{subsec:NumSimIEEEBus}. The $5$ rows above correspond to the $5$ generator nodes; these are buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. The columns correspond to the time snapshots. The colorbar at the bottom shows the marginal PDF values.}}
\vspace*{-0.1in}
\label{fig:IEEE14marginals}
\end{figure*}

@@

% Proximal algorithm
% =====================================
\bibitem{parikh2014proximal}
N.~Parikh, and S.~Boyd, ``Proximal Algorithms", \emph{Foundations and Trends in Optimization}, Vol. 1, No. 3, pp. 127--239, 2014.

@@

\bibitem{mardia2009directional}
K.V.~Mardia, and P.E.~Jupp, \emph{Directional Statistics}, Wiley, 1st edition, 1999.
